Unveiling Exception Handling Bug Hazards in Android based on GitHub and Google Code Issues

### 2015-02-16 android-stacks.tex
correcting a typpo

\emph{\textbf{Exception Type Analysis.}} To support a deeper investigation of the 
stack traces every exception defined on a stack trace needs to be classified according to its type
(e.g. Error, checked Exception or RuntimeException). The module responsible for this analysis 
uses the Design Wizard framework \cite{Brunet09} to inspect the bytecode of the exceptions reported 
on stack traces.  It walks up the type hierarchy of a Java exception until it reaches 
a base exception type. Hence in this study the bytecode analysis was only used to discover the type 
of each mined exception when the jar file of such exception was available on the project or 
on the reused core Java libraries. An specific implementation (based on source code analysis)
 was needed to to discover the exception type when the bytecode was not available.

>>>>

\emph{\textbf{Exception Type Analysis.}} To support a deeper investigation of the 
stack traces every exception defined on a stack trace needs to be classified according to its type
(e.g. Error, checked Exception or RuntimeException). The module responsible for this analysis 
uses the Design Wizard framework \cite{Brunet09} to inspect the bytecode of the exceptions reported 
on stack traces.  It walks up the type hierarchy of a Java exception until it reaches 
a base exception type. Hence in this study the bytecode analysis was used to discover the type 
of each mined exception when the jar file of such exception was available on the project or 
on a reused  Java library. An specific implementation (based on source code analysis)
 was needed to discover the exception type when the bytecode was not available.
